Boundary Labeling for annotated documents

### 2018-06-17 LaTeX/Paper.tex
Paper: Edited Abstract. Program: No changes.

\begin{abstract}
	In this paper, we present an algorithm capable of solving the one-sided boundary-labeling problem for crossing-free, monotonous OPO-Leaders in $O(n^2)$ using only the space between words and lines. We prove its correctness and evaluate its performance under different conditions.
\end{abstract}

>>>>

\begin{abstract}
	The applications of Boundary Labeling in tests are largely unexplored and existing solutions often impact readability or produce ambiguous labelings.

	In this paper, we present an algorithm that produces crossing-free, monotonous OPO-Leaders and solves the one-sided boundary-labeling problem in $O(n^2)$.
	We also prove its correctness and evaluate the performance under different circumstances.
	%In this paper, we present an algorithm capable of solving the one-sided boundary-labeling problem for crossing-free, monotonous OPO-Leaders in $O(n^2)$ using only the space between words and lines. We prove its correctness and evaluate its performance under different conditions.
\end{abstract}
